\documentclass{article}
\usepackage{tikz}
\usepackage{amsmath}

\begin{document}
(7th March)
\section*{Arithmetic Progression Graphs}
Cover the brute force approach before iterating. $G = (V, E)$ where we label with weights each $v \in V$ and $e \in E$. ie. $L_1 : V \rightarrow Z+$, where $Z+$ are just positive integers. We say $L_1$ are the vertex labels, $L_2$ are the edge labels.

\begin{itemize}
				\item Each vertex labels are the sum of it's incident edge labels. So $L_1(v) = \sum_{u \in N(v)} L_2(uv)$.
				\item These vertex labels if looped (sorted) would have the shape $\{a, a+d,...,a+(n-1)d\}$ where $n=|V|$
\end{itemize}

"An APG with parameters $a$ and $d$".

So the question we have is "given a description of a graph" does there exist a labeling such that the vertices form a APG.

\subsection*{Properties}

With $n = |V|$ and $m = |E|$ and arithmetic progression parameters positive;
\begin{itemize}
				\item $a \geq $ the minimum vertex degree in $G$. (vertex of graph with least incident edges).
				\item Sum of edge labels is half of the sum of the vertex labels.
				\item Given $a,d$ parameters of an APG, $s_v = na + (0 + 1 + ... + (n-1)d) = na + \frac{n(n-1)}{2}d$
				\item $2na + n(n-1)d$ is divisible by 4 (multiplying a known even $s_v$ by 2)
				\item $s_e = (2na + n(n-1)d) / 4 \geq m$
\end{itemize}

All of those should make sense... So now we know $s_e$, the problem is to tweak numbers $a$ and $d$ whilst dealing with paritionings.

\subsection*{Solution 1 - Combinatorial}
Check all combinations of edge labels that sum up to $s_e = (2na + n(n-1)d)/4$. This is the same as checking all integer paritions of $s_e$ with $m = |E|$ parts.

\subsection*{Solution 2 - Solving Systems of Equations}
(28min)

\subsection*{Solution 3 - Augmenting Paths Approach}
Improving walk technique... (43min)

\subsubsection*{Not hugely important to take everything in here}
Mostly to get familiar with the general idea of integer programming so perhaps we create seperate section for just that.

\end{document}
